Haul-out behavior and aerial survey detectability of seals in the Bering and Chukchi seas

### 2022-01-26 README.Rmd
UPDATE ACKNOWLEDGEMENTS

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered MS Word version,
    `London_HauloutBehavior.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: figures](/analysis/figures): figures generated
  - [:file\_folder: templates](/analysis/templates): template files and scripts.

@@

>>>>

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered as a PDF,
    [London_HauloutBehavior.pdf](https://github.com/jmlondon/berchukHaulout/blob/main/analysis/paper/London_HauloutBeahvior.pdf), suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: figures](/analysis/figures): figures generated
  - [:file\_folder: templates](/analysis/templates): template files and scripts.

@@

## Acknowledgements

We recognize that the species and ecosystems studied in this paper are within
the traditional range of the Inpuiaq and Yupik people. And, we would like to
acknowledge and thank them as the original stewards of these ecosystems. The
deployment of bio-logging devices used in this study were often done in
collaboration with Alaska Native seal hunters near their communities. We would
like to especially acknowledge the communities of Kotzebue, Koyuk, Nome,
Nuiqsut, Scammon Bay, St. Michael, Utqiaġvik, and Ulguniq (Wainwright) and the
following individuals: James Adams, Jeff Barger, David Barr, Wendell Booth,
Cyrus Harris, Nereus 'Doc' Harris, Grover Harris, Lee Harris, Tom Jones, Frank
Garfield, Brenda Goodwin, Henry Goodwin, John Goodwin, Pearl Goodwin, Willie
Goodwin, Brett Kirk, Noah Naylor, Virgil Naylor Jr., Virgil Naylor Sr., Dan
Savetilik, Chuck Schaeffer, Ross Schaeffer, Allen Stone, and Randy Toshavik from
Kotzebue, Alaska; Merlin Henry from Koyuk, Alaska; Tom Gray from Nome; Vernon
Long and Richard Tukle from Nuiqsuit, Alaska; Morgan Simon, River Simon, and Al
Smith from Scammon Bay, Alaska; Alex Niksik Jr. from St. Michael, Alaska; Billy
Adams, James Aiken, Tim Aiken, Howard Kittick, Gilbert Leavitt, Isaac Leavitt,
J.R. Leavitt, and Joe Skin from Utqiaġvik, Alaska; Mary Ellen Ahmaogak, Enoch
Oktollik, Shawn Oktollik, Stacey Osborn, and Fred Rexford from Ulguniq, Alaska.

We are grateful for the assistance in catching and sampling seals by Ryan Adam,
James Bailey, Michelle Barbieri, John Bengtson, Gavin Brady, Vladamir Burkanov,
Cynthia Christman, Sarah Coburn, Shawn Dahle, Rob Delong, Stacy DiRocco, Deb
Fauquier, Shannon Fitzgerald, Kathy Frost, Scott Gende, Tracey Goldstein, Jeff
Harris, Jason Herreman, Markus Horning, John Jansen, Shawn Johnson, Charles
Littnan, Lloyd Lowry, Brett McClintock, Erin Moreland, Mark Nelson, Justin
Olnes, Lorrie Rea, Bob Shears, Gay Sheffield, Brent Stewart, Dave Withrow, and
Heather Ziel. We also appreciate the commitment to science and safety by all
officers and crew of the NOAA Ship Oscar Dyson, the NOAA Ship MacArthur II, and
the RV Thomas G. Thompson.

Telemetry data from the Alaska Department of Fish and Game (ADFG) and the North
Slope Borough Department of Wildlife Management (NSB) were important
contributions to the findings presented here. Both agencies collaborate closely
with Alaska Native communities and the contributions of local hunters to the
successful capture, deployment, and understanding of seal ecology are
invaluable. Deployments in the western Bering Sea were done in collaboration
with Russian colleagues and North Pacific Wildlife.

### 2022-01-26 analysis/paper/London_HauloutBeahvior.Rmd
UPDATE ACKNOWLEDGEMENTS

We recognize that the species and ecosystems studied in this paper are within
the traditional range of the Inpuiaq and Yupik people. And, we would like to
acknowledge and thank them as the original stewards of these ecosystems. The
deployment of bio-logging devices used in this study were often done in
collaboration with Alaska Native seal hunters near their communities. We would
like to especially acknowledge the communities of Kotzebue, Koyuk, Nome,
Nuiqsut, Scammon Bay, St. Michael, Utqiaġvik, and Ulguniq (Wainwright) and the
following individuals: James Adams, Jeff Barger, David Barr, Wendell Booth,
Cyrus Harris, Nereus 'Doc' Harris, Grover Harris, Lee Harris, Tom Jones, Frank
Garfield, Brenda Goodwin, Henry Goodwin, John Goodwin, Pearl Goodwin, Willie
Goodwin, Brett Kirk, Noah Naylor, Virgil Naylor Jr., Virgil Naylor Sr., Dan
Savetilik, Chuck Shaeffer, Ross Schaeffer, Allen Stone, and Randy Toshavik from
Kotzebue, Alaska; Merlin Henry from Koyuk, Alaska; Tom Gray from Nome; Vernon
Long and Richard Tukle from Nuiqsuit, Alaska; Morgan Simon, River Simon, and Al
Smith from Scammon Bay, Alaska; Alex Niksik Jr. from St. Michael, Alaska; Billy
Adams, James Aiken, Tim Aiken, Howard Kittick, Gilbert Leavitt, Isaac Leavitt,
Joe Skin from Utqiaġvik, Alaska; Mary Ellen Ahmaogak, Enoch Oktollik, Shawn
Oktollik, Stacey Osborn, and Fred Rexford from Ulguniq, Alaska.

>>>>

We recognize that the species and ecosystems studied in this paper are within
the traditional range of the Inpuiaq and Yupik people. And, we would like to
acknowledge and thank them as the original stewards of these ecosystems. The
deployment of bio-logging devices used in this study were often done in
collaboration with Alaska Native seal hunters near their communities. We would
like to especially acknowledge the communities of Kotzebue, Koyuk, Nome,
Nuiqsut, Scammon Bay, St. Michael, Utqiaġvik, and Ulguniq (Wainwright) and the
following individuals: James Adams, Jeff Barger, David Barr, Wendell Booth,
Cyrus Harris, Nereus 'Doc' Harris, Grover Harris, Lee Harris, Tom Jones, Frank
Garfield, Brenda Goodwin, Henry Goodwin, John Goodwin, Pearl Goodwin, Willie
Goodwin, Brett Kirk, Noah Naylor, Virgil Naylor Jr., Virgil Naylor Sr., Dan
Savetilik, Chuck Schaeffer, Ross Schaeffer, Allen Stone, and Randy Toshavik from
Kotzebue, Alaska; Merlin Henry from Koyuk, Alaska; Tom Gray from Nome; Vernon
Long and Richard Tukle from Nuiqsuit, Alaska; Morgan Simon, River Simon, and Al
Smith from Scammon Bay, Alaska; Alex Niksik Jr. from St. Michael, Alaska; Billy
Adams, James Aiken, Tim Aiken, Howard Kittick, Gilbert Leavitt, Isaac Leavitt,
J.R. Leavitt, and Joe Skin from Utqiaġvik, Alaska; Mary Ellen Ahmaogak, Enoch Oktollik, Shawn
Oktollik, Stacey Osborn, and Fred Rexford from Ulguniq, Alaska.
